Model

### 2020-03-25 analysis/polygenic_model.Rmd
polygenic done

## Model
 $$Y = \tilde{X}\gamma + G\theta + \epsilon$$
$Y$: quantitative traits, $N$ x 1 vector, $N$ is number of individuals  
$\tilde{X}$: imputed gene expression (standardized). $N$ x $J$ matrix, $J$ is number of genes.  
$G$: genotype (standardized). $N$ x $M$ matrix, $M$ is number of SNPs.  
$\gamma$: effect sizes for $\tilde{X}$,  $\gamma_j$, effect size for gene $j$.

@@

## Model inference
The above model is equivalent to this: 
$$Y \sim N(0,\sigma_\gamma^2XX^T + \sigma_\theta^2GG^T + \sigma_e^2I) $$
This is REML with multiple (more than 2) variance components. Use HE regression function from GEMMA software.

>>>>

## Polygenic Model
 $$Y = \tilde{X}\gamma + G\theta + \epsilon$$
$Y$: quantitative traits, $N$ x 1 vector, $N$ is number of individuals  
$\tilde{X}$: imputed gene expression (standardized). $N$ x $J$ matrix, $J$ is number of genes.  
$G$: genotype (standardized). $N$ x $M$ matrix, $M$ is number of SNPs.  
$\gamma$: effect sizes for $\tilde{X}$,  $\gamma_j$, effect size for gene $j$.

@@

## Polygenic Model Inference
The above model is equivalent to this: 
$$Y \sim N(0,\sigma_\gamma^2XX^T + \sigma_\theta^2GG^T + \sigma_e^2I) $$
This is REML with multiple (more than 2) variance components. Use HE regression function from GEMMA software.
